Coherent optical creation of a single molecule

### 2020-12-09 paper.tex
Update on Overleaf.

\begin{figure}
  \includegraphics[width=0.5\textwidth]{imgs/raman_spectroscopy_raman_beampath.pdf}
  \caption{
    Beam path for generating two frequencies in the tweezer for the Raman transition (only essential optics shown.)
    Two  filters, one directly after the laser source and one after both optical fibers clean the light from a fiber amplifier seeded by an external cavity diode laser.
    The red beam path is the always-present $0^{\mathrm{th}}$ order of the double pass~(DP) AOM.
    The blue beam path is the switchable $1^{\mathrm{st}}$ order of the DP AOM. It generates the second frequency for the Raman transition.
    % When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
    % (blue beam path) which generates the required frequency different to drive
    % the Raman transition.
    % The two frequencies are recombined on the DP AOM.
    To reduce power fluctuations, the $0^{\mathrm{th}}$ order light is shifted by another single pass~(SP) AOM before recombination, preventing interference with leakage light from the DP AOM~[[TR: What frequency is the leakage light? ]].
    % be at the same frequency
    % as the $0$-th order light which can cause a significant power fluctuation
    % due to interference.
    The experiment typically starts with the SP AOM on and the DP AOM off.
    When driving the Raman transition, the RF powers for both AOMs are ramped simultaneously
    to achieve the desired power at both frequencies, while keeping the total power fixed.
    \label{f-beampath}
  }
\end{figure}

@@

The molecular lifetime of $0.199(9)~\mathrm{ms}$ in Fig.~\ref{f-lifetime}a is measured by preparing the molecule with a $\pi$-pulse,
followed after a variable delay by a second dissociating $\pi$-pulse.
This result is
consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b. Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.  Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the two-body lifetimes of the atoms directly without the second Raman frequency. In principle, destructive interference that reduces the Raman Rabi rate ($\Omega_{\rm R}$) for negative detunings ($\Delta$) changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.  More negative detunings than XXX~GHz that might reduce the scattering rate were prevented by vanishing of $\Omega_{\rm R}$.

>>>>

\begin{figure}
  \includegraphics[width=0.5\textwidth]{imgs/raman_spectroscopy_raman_beampath.pdf}
  \caption{
    Beam path for generating two frequencies in the tweezer for the Raman transition (only essential optics shown.)
    Two  filters, one directly after the laser source and one after both optical fibers clean the light from a fiber amplifier seeded by an external cavity diode laser.
    The red beam path is the always-present $0^{\mathrm{th}}$ order of the double pass~(DP) AOM.
    The blue beam path is the switchable $1^{\mathrm{st}}$ order of the DP AOM. It generates the second frequency for the Raman transition.
    % When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
    % (blue beam path) which generates the required frequency different to drive
    % the Raman transition.
    % The two frequencies are recombined on the DP AOM.
    To reduce interferences that cause relative power fluctuation of the two frequencies, the $0^{\mathrm{th}}$ order is frequency shifted by $-80$~MHz before recombination.
    % be at the same frequency
    % as the $0$-th order light which can cause a significant power fluctuation
    % due to interference.
    The experiment typically starts with the single-pass (SP) AOM on and the DP AOM off.
    When driving the Raman transition, the RF powers for both AOMs are ramped simultaneously
    to achieve the desired optical power at both frequencies, while keeping the total optical power fixed.
    \label{f-beampath}
  }
\end{figure}

@@

The molecular lifetime of $0.199(9)~\mathrm{ms}$ in Fig.~\ref{f-lifetime}a is measured by preparing the molecule with a $\pi$-pulse,
followed after a variable delay by a second dissociating $\pi$-pulse.
This result is
consistent with the decay of the Rabi oscillation in Fig.~\ref{f-raman}b. Preliminary experiments and theoretical considerations indicate that the molecular lifetime may be limited by two-photon coupling to the atomic continuum~\cite{YichaoYu}.  Atom loss is shown to be small in Fig.~\ref{f-lifetime}b by measuring the two-body lifetimes of the atoms directly without the second Raman frequency. In principle, destructive interference that reduces the Raman Rabi rate ($\Omega_{\rm R}$) for negative detunings ($\Delta$) changes to constructive interference for positive detunings, but additional molecular resonances make the positive region unusable.  More negative detunings that might reduce the scattering rate were prevented by vanishing of $\Omega_{\rm R}$.
